Classifying Human Driving Behavior via Deep Neural Networks

### 2017-05-30 paper/paper-DrexelFormat.tex
updated paper - reduce result data

\section{Experiments with {\em raw dataset}}
The second part of experiments used {\em raw dataset} which has 98 features. The dataset was re-sampled only by 1 over 10 with {\em last} method. This is because the test time with {\em second model} with SAE and {\em third model} with MAE took much more than the test time with {\em first model} and from the result of the first part of experiments, the best overall performance was from 1 over 10 re-sampled data and the best performance was from {\em last} method.

\subsection{Comparison of results from three models}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/compare_result_last_1_10.png}
    \caption{Result of three models with {\em last} method}
    \label{fig:compare_result_last_1_10}
\end{figure}

Figure \ref{fig:compare_result_last_1_10} compares the performance from the reduced dimensions data by human, MAE, and SAE. Table \ref{tbl:mae_last_1_10} and Table \ref{tbl:sae_last_1_10} show the detailed result of MAE and SAE respectively and Table \ref{tbl:mae_last_1_10_time} and Table \ref{tbl:sae_last_1_10_time} shows the test time for MAE and SAE respectively.

The overall average accuracy from SAE is 0.3375 (33.75\%) and the overall average accuracy from MAE is 0.428125 (42.8125\%). Both performance are much lower than 0.540625 (54.0625\%) performance from the experiments with data filtered by human. Next subsection explains the reasons why SAE and MAE gave worse performance.

\begin{table}[!t]
\centering
\caption{MAE, {\em last} method on 1 over 10 Re-sampled {\em raw dataset}}
\label{tbl:mae_last_1_10}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.25         & 0.75         & 0.25         & 0            & 0.5          \\ \cline{2-7}
                      & 2                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
                      & 3                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
                      & 4                   & 0.25         & 0.25         & 0.5          & 0.5          & 0.5          \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.75         & 0.75         & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
                      & 2                   & 0.5          & 1            & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
                      & 3                   & 0.25         & 0.25         & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
                      & 4                   & 0.25         & 0.75         & 0.25         & 0.25         & 0.5          \\ \hline
\multirow{4}{*}{3}    & 1                   & 0            & 0.25         & 0.75         & 0            & 0.5          \\ \cline{2-7}
                      & 2                   & 0.25         & 0.5          & 0.25         & 0.5          & 0.25         \\ \cline{2-7}
                      & 3                   & 0.25         & 0.25         & 0.75         & 0.5          & 0.25         \\ \cline{2-7}
                      & 4                   & 1            & 0.5          & 0.5          & 0.5          & 0.5          \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5          & 0.5          & 0.25         & 0.5          & 0.75         \\ \cline{2-7}
                      & 2                   & 0            & 0.5          & 0.5          & 0.25         & 0.25         \\ \cline{2-7}
                      & 3                   & 0            & 0.25         & 0            & 0.25         & 0.5          \\ \cline{2-7}
                      & 4                   & 0.5          & 0            & 0.5          & 0.5          & 0.25         \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.359375     & 0.46875      & 0.453125     & 0.40625      & 0.453125     \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.2733854117 & 0.2561737691 & 0.2085415626 & 0.2015564437 & 0.1359764073 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{MAE, {\em last} Test Time with 1 over 10 Re-sampled {\em raw dataset}}
\label{tbl:mae_last_1_10_time}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multicolumn{5}{c|}{The number of neurons}       \\ \cline{2-6}
                      & 16      & 32      & 64      & 128     & 256      \\ \hline
1                     & 6:59:30 & 6:59:33 & 8:13:06 & 9:21:31 & 11:40:13 \\ \hline
2                     & 6:25:43 & 6:58:03 & 7:50:26 & 8:52:23 & 11:06:24 \\ \hline
3                     & 6:14:18 & 6:43:07 & 7:12:21 & 8:17:23 & 10:17:59 \\ \hline
4                     & 7:07:35 & 4:52:05 & 5:28:28 & 6:38:07 & 8:43:28  \\ \hline
Mean                  & 6:41:47 & 6:23:12 & 7:11:05 & 8:17:21 & 10:27:01 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{SAE, {\em last} method on 1 over 10 Re-sampled {\em raw dataset}}
\label{tbl:sae_last_1_10}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{5}{c|}{The number of neurons}                               \\ \cline{3-7}
                      &                     & 16           & 32           & 64           & 128          & 256          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.75         & 0.75         & 0.5          & 0            & 0.5          \\ \cline{2-7}
                      & 2                   & 0.25         & 0            & 0.5          & 0.25         & 0.25         \\ \cline{2-7}
                      & 3                   & 0.75         & 0            & 0            & 0.25         & 0.5          \\ \cline{2-7}
                      & 4                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.75         \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5          & 0.5          & 0.25         & 0.75         & 0.5          \\ \cline{2-7}
                      & 2                   & 0.5          & 0.25         & 0            & 0            & 0            \\ \cline{2-7}
                      & 3                   & 0.5          & 0            & 0.25         & 0.5          & 0.75         \\ \cline{2-7}
                      & 4                   & 0.25         & 0.75         & 0.5          & 0.5          & 0            \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.25         & 0.25         & 0.5          & 0.25         & 0            \\ \cline{2-7}
                      & 2                   & 0.25         & 0.25         & 0.5          & 0.25         & 0.5          \\ \cline{2-7}
                      & 3                   & 0.25         & 0.25         & 0.25         & 0.25         & 0.25         \\ \cline{2-7}
                      & 4                   & 0.75         & 0.5          & 0.25         & 0            & 0            \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5          & 0.25         & 0.25         & 0.25         & 0.25         \\ \cline{2-7}
                      & 2                   & 0.25         & 0.75         & 0            & 0.5          & 0            \\ \cline{2-7}
                      & 3                   & 0.25         & 0.25         & 0.5          & 0            & 0            \\ \cline{2-7}
                      & 4                   & 0.25         & 0.5          & 0.75         & 0.25         & 0.25         \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.421875     & 0.359375     & 0.34375      & 0.28125      & 0.28125      \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2576941016 & 0.2212653008 & 0.2212653008 & 0.2719528145 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{SAE, {\em last} Test Time with 1 over 10 Re-sampled {\em raw dataset}}
\label{tbl:sae_last_1_10_time}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multicolumn{5}{c|}{The number of neurons}      \\ \cline{2-6}
                      & 16      & 32      & 64      & 128     & 256     \\ \hline
1                     & 4:20:50 & 4:58:12 & 7:44:27 & 6:42:45 & 8:38:18 \\ \hline
2                     & 3:48:20 & 3:51:03 & 5:16:07 & 6:02:29 & 8:24:17 \\ \hline
3                     & 3:50:54 & 4:47:55 & 5:03:59 & 6:29:31 & 8:48:47 \\ \hline
4                     & 3:40:38 & 4:09:14 & 4:56:10 & 6:09:21 & 8:24:11 \\ \hline
Mean                  & 3:55:11 & 4:26:36 & 5:45:11 & 6:21:02 & 8:33:53 \\ \hline
\end{tabular}
\end{table}

\subsection{Analysis Training LSTM in {\em second model} and {\em third model}}
The difference between {\em first model} and other models is that other models have AE. Therefore, AE layer from {\em second model} and {\em third model} caused worse performance. The first evidence of this can be found during training LSTM in both models. Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show the accuracy of the result from LSTM on each iterations during training. Figure \ref{fig:sae_loss} and Figure \ref{fig:mae_loss} show the loss (error) on each iterations during training. Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show the details of the train accuracy from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Table \ref{tbl:sae_16_loss}, Table \ref{tbl:sae_32_loss}, Table \ref{tbl:sae_64_loss}, Table \ref{tbl:sae_128_loss}, and Table \ref{tbl:sae_256_loss} show the details of the train loss from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Table \ref{tbl:mae_16_accuracy}, Table \ref{tbl:mae_32_accuracy}, Table \ref{tbl:mae_64_accuracy}, Table \ref{tbl:mae_128_accuracy}, and Table \ref{tbl:mae_256_accuracy} show the details of the train accuracy from {\em third model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Table \ref{tbl:mae_16_loss}, Table \ref{tbl:mae_32_loss}, Table \ref{tbl:mae_64_loss}, Table \ref{tbl:mae_128_loss}, and Table \ref{tbl:mae_256_loss} show the details of the train loss from {\em third model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.

@@

\begin{table}[!t]
\centering
\caption{SAE, 16 Neuron Training Accuracy}
\label{tbl:sae_16_accuracy}
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                \\ \cline{3-11}
                      &                     & 0             & 120         & 240           & 360          & 480          & 600                              & 720                               & 840          & 960          \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.58333       & 0.66667     & 0.66667       & 0.75         & 0.75         & 0.83333                          & 1                                 & 0.91667      & 0.91667      \\ \cline{2-11}
                      & 2                   & 0.5           & 0.5         & 0.66667       & 0.83333      & 0.83333      & 0.91667                          & 1                                 & 1            & 1            \\ \cline{2-11}
                      & 3                   & 0.41667       & 0.58333     & 0.66667       & 0.91667      & 0.83333      & 0.83333                          & 0.91667                           & 1            & 0.91667      \\ \cline{2-11}
                      & 4                   & 0.5           & 0.58333     & 0.58333       & 0.58333      & 0.58333      & 0.75                             & 0.91667                           & 0.91667      & 0.91667      \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5           & 0.58333     & 0.5           & 0.5          & 0.5          & 0.58333                          & 0.75                              & 0.75         & 0.83333      \\ \cline{2-11}
                      & 2                   & 0.5           & 0.58333     & 0.75          & 0.75         & 0.83333      & 0.91667                          & 1                                 & 1            & 1            \\ \cline{2-11}
                      & 3                   & 0.5           & 0.66667     & 0.75          & 0.75         & 0.83333      & 0.91667                          & 0.83333                           & 0.83333      & 0.91667      \\ \cline{2-11}
                      & 4                   & 0.5           & 0.5         & 0.5           & 0.5          & 0.58333      & 0.5                              & 0.58333                           & 0.66667      & 0.66667      \\ \hline
\multirow{4}{*}{3}    & 1                   & 0.5           & 0.5         & 0.58333       & 0.58333      & 0.75         & 0.58333                          & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
                      & 2                   & 0.5           & 0.41667     & 0.5           & 0.66667      & 0.66667      & 0.75                             & 0.75                              & 0.75         & 0.91667      \\ \cline{2-11}
                      & 3                   & 0.5           & 0.33333     & 0.5           & 0.41667      & 0.5          & 0.58333                          & 0.91667                           & 0.75         & 0.75         \\ \cline{2-11}
                      & 4                   & 0.33333       & 0.66667     & 0.66667       & 0.66667      & 0.83333      & 0.83333                          & 0.91667                           & 1            & 1            \\ \hline
\multirow{4}{*}{4}    & 1                   & 0.5           & 0.58333     & 0.58333       & 0.66667      & 0.75         & 0.83333                          & 0.83333                           & 0.83333      & 0.75         \\ \cline{2-11}
                      & 2                   & 0.5           & 0.33333     & 0.66667       & 0.83333      & 0.66667      & 0.75                             & 0.75                              & 0.66667      & 0.83333      \\ \cline{2-11}
                      & 3                   & 0.41667       & 0.58333     & 0.66667       & 0.66667      & 0.75         & 0.83333                          & 0.91667                           & 0.91667      & 0.91667      \\ \cline{2-11}
                      & 4                   & 0.5           & 0.41667     & 0.5           & 0.66667      & 0.75         & 0.75                             & 0.75                              & 0.83333      & 0.75         \\ \hline
\multicolumn{2}{|c|}{Mean}                  & 0.484375      & 0.531249375 & 0.609375625   & 0.671875625  & 0.713540625  & 0.760415625                      & 0.838541875                       & 0.84895875   & 0.8697925    \\ \hline
\multicolumn{2}{|c|}{Std}                   & 0.05459200528 & 0.109185219 & 0.08985045449 & 0.1342629486 & 0.1177274886 & \multicolumn{1}{l|}{0.132201113} & \multicolumn{1}{l|}{0.1342647589} & 0.1187071365 & 0.1007786353 \\ \hline
\end{tabular}}
\end{table}

\begin{table}[!t]
\centering
\caption{SAE, 32 Neuron Training Accuracy}
\label{tbl:sae_32_accuracy}
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                 \\ \cline{3-11}
                      &                     & 0             & 120          & 240          & 360          & 480          & 600                              & 720                               & 840          & 960           \\ \hline
\multirow{4}{*}{1}    & 1                   & 0.41667       & 0.66667      & 0.91667      & 0.91667      & 0.83333      & 0.91667                          & 1                                 & 0.91667      & 1             \\ \cline{2-11}
                      & 2                   & 0.5           & 0.75         & 0.66667      & 0.75         & 0.83333      & 1                                & 1                                 & 1            & 1             \\ \cline{2-11}
                      & 3                   & 0.5           & 0.75         & 0.66667      & 0.75         & 0.91667      & 1                                & 0.91667                           & 0.58333      & 0.75          \\ \cline{2-11}
                      & 4                   & 0.5           & 0.58333      & 0.66667      & 0.66667      & 0.91667      & 0.91667                          & 1                                 & 1            & 1             \\ \hline
\multirow{4}{*}{2}    & 1                   & 0.5           & 0.75         & 0.83333      & 0.83333      & 0.91667      & 1                                & 0.91667                           & 0.91667      & 1             \\ \cline{2-11}
                      & 2                   & 0.41667       & 0.58333      & 0.83333      & 0.91667      & 1            & 0.91667                          & 1                                 & 0.91667      & 1             \\ \cline{2-11}
                      & 3                   & 0.5           & 0.66667      & 0.58333      & 0.66667      & 0.66667      & 0.66667                          & 0.75                              & 0.75         & 0.83333       \\ \cline{2-11}
                      & 4                   & 0.5           & 0.33333      & 0.41667      & 0.5          & 0.5          & 0.83333                          & 0.58333                           & 0.83333      & 0.83333       \\ \hline

>>>>

\section{Experiments with {\em raw dataset}}
The second part of experiments used {\em raw dataset} which has 98 features. The dataset was re-sampled only by 1 over 10 with {\em last} method. This is because the experiment time with {\em second model} with SAE and {\em third model} with MAE took much more than the experiment time with {\em first model}, and from the result of the first part of experiments, the best overall performance was from 1 over 10 re-sampled data and the best performance was from {\em last} method. The {\em second model} and {\em third model} were also tested four times with different number of neurons in LSTM hidden layer: 16, 32, 64, 128, and 256 neurons. The purpose of the second part of experiments is performance comparison between three different ways to reduce dimensions: human({\em first model}), SAE({\em second model}), and MAE({\em third model}).

\subsection{Comparison of results from three models}
Figure \ref{fig:compare_result_last_1_10} compares accuracy of three models with data reduced dimensions by human, SAE, and MAE respectively. Table \ref{tbl:compare_accuracy_last_1_10} shows accuracy of three models, Table \ref{tbl:compare_std_last_1_10} shows detail standard deviation of three models, and Table \ref{tbl:compare_time_last_1_10} shows test time of three models.

The overall average accuracy from SAE is 0.3375 (33.75\%) and the overall average accuracy from MAE is 0.428125 (42.8125\%). Both performance are much lower than 0.55625 (55.625\%) performance from the experiments with data filtered by human. Next subsection explains the reasons why SAE and MAE gave worse performance.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.75\textwidth]{pictures/result_pictures/compare_result_last_1_10.png}
    \caption{Result of three models with {\em last} method}
    \label{fig:compare_result_last_1_10}
\end{figure}

\begin{table}[!t]
\centering
\caption{Accuracy of three models with {\em last} method}
\label{tbl:compare_accuracy_last_1_10}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Average         & \multicolumn{6}{c|}{The number of neurons}                     \\ \hline
Model           & 16       & 32       & 64       & 128     & 256      & Average  \\ \hline
\textit{first}  & 0.5      & 0.5      & 0.6875   & 0.59375 & 0.5      & 0.55625  \\ \hline
\textit{second} & 0.421875 & 0.359375 & 0.34375  & 0.28125 & 0.28125  & 0.3375   \\ \hline
\textit{third}  & 0.359375 & 0.46875  & 0.453125 & 0.40625 & 0.453125 & 0.428125 \\ \hline
\end{tabular}
\end{table}

\begin{table}[!t]
\centering
\caption{Standard Deviation of three models with {\em last} method}
\label{tbl:compare_std_last_1_10}
\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Std.            & \multicolumn{6}{c|}{The number of neurons}                                              \\ \hline
Model           & 16           & 32           & 64           & 128          & 256          & Average      \\ \hline
\textit{first}  & 0.2581988897 & 0.2041241452 & 0.2140872096 & 0.2015564437 & 0.2236067977 & 0.2203146972 \\ \hline
\textit{second} & 0.1983000672 & 0.2576941016 & 0.2212653008 & 0.2212653008 & 0.2719528145 & 0.234095517  \\ \hline
\textit{third}  & 0.2733854117 & 0.2561737691 & 0.2085415626 & 0.2015564437 & 0.1359764073 & 0.2151267189 \\ \hline
\end{tabular}}
\end{table}

\begin{table}[!t]
\centering
\caption{Test Time of three models with {\em last} method}
\label{tbl:compare_time_last_1_10}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Std.            & \multicolumn{6}{c|}{The number of neurons}                 \\ \hline
Model           & 16      & 32      & 64      & 128     & 256      & Average \\ \hline
\textit{first}  & 2:11:58 & 2:21:11 & 3:04:34 & 4:28:24 & 6:35:52  & 3:44:24 \\ \hline
\textit{second} & 3:55:11 & 4:26:36 & 5:45:11 & 6:21:02 & 8:33:53  & 5:48:23 \\ \hline
\textit{third}  & 6:41:47 & 6:23:12 & 7:11:05 & 8:17:21 & 10:27:01 & 7:48:05 \\ \hline
\end{tabular}
\end{table}
%\caption{MAE, {\em last} method on 1 over 10 Re-sampled {\em raw dataset}}
%\label{tbl:mae_last_1_10}
%\multirow{4}{*}{1}    & 1                   & 0.25         & 0.75         & 0.25         & 0            & 0.5          \\ \cline{2-7}
%                      & 2                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
%                      & 3                   & 0.5          & 0.5          & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
%                      & 4                   & 0.25         & 0.25         & 0.5          & 0.5          & 0.5          \\ \hline
%\multirow{4}{*}{2}    & 1                   & 0.75         & 0.75         & 0.5          & 0.75         & 0.5          \\ \cline{2-7}
%                      & 2                   & 0.5          & 1            & 0.5          & 0.5          & 0.5          \\ \cline{2-7}
%                      & 3                   & 0.25         & 0.25         & 0.75         & 0.5          & 0.5          \\ \cline{2-7}
%                      & 4                   & 0.25         & 0.75         & 0.25         & 0.25         & 0.5          \\ \hline
%\multirow{4}{*}{3}    & 1                   & 0            & 0.25         & 0.75         & 0            & 0.5          \\ \cline{2-7}
%                      & 3                   & 0.25         & 0.25         & 0.75         & 0.5          & 0.25         \\ \cline{2-7}
%                      & 4                   & 1            & 0.5          & 0.5          & 0.5          & 0.5          \\ \hline
%\multirow{4}{*}{4}    & 1                   & 0.5          & 0.5          & 0.25         & 0.5          & 0.75         \\ \cline{2-7}
%                      & 2                   & 0            & 0.5          & 0.5          & 0.25         & 0.25         \\ \cline{2-7}
%                      & 3                   & 0            & 0.25         & 0            & 0.25         & 0.5          \\ \cline{2-7}
%                      & 4                   & 0.5          & 0            & 0.5          & 0.5          & 0.25         \\ \hline
%\multicolumn{2}{|c|}{Mean}                  & 0.359375     & 0.46875      & 0.453125     & 0.40625      & 0.453125     \\ \hline
%\multicolumn{2}{|c|}{Std}                   & 0.2733854117 & 0.2561737691 & 0.2085415626 & 0.2015564437 & 0.1359764073 \\ \hline
%\caption{MAE, {\em last} Test Time with 1 over 10 Re-sampled {\em raw dataset}}
%\label{tbl:mae_last_1_10_time}
%1                     & 6:59:30 & 6:59:33 & 8:13:06 & 9:21:31 & 11:40:13 \\ \hline
%2                     & 6:25:43 & 6:58:03 & 7:50:26 & 8:52:23 & 11:06:24 \\ \hline
%3                     & 6:14:18 & 6:43:07 & 7:12:21 & 8:17:23 & 10:17:59 \\ \hline
%4                     & 7:07:35 & 4:52:05 & 5:28:28 & 6:38:07 & 8:43:28  \\ \hline
%Mean                  & 6:41:47 & 6:23:12 & 7:11:05 & 8:17:21 & 10:27:01 \\ \hline
%\caption{SAE, {\em last} method on 1 over 10 Re-sampled {\em raw dataset}}
%\label{tbl:sae_last_1_10}
%\multirow{4}{*}{1}    & 1                   & 0.75         & 0.75         & 0.5          & 0            & 0.5          \\ \cline{2-7}
%                      & 2                   & 0.25         & 0            & 0.5          & 0.25         & 0.25         \\ \cline{2-7}
%                      & 3                   & 0.75         & 0            & 0            & 0.25         & 0.5          \\ \cline{2-7}
%\multirow{4}{*}{2}    & 1                   & 0.5          & 0.5          & 0.25         & 0.75         & 0.5          \\ \cline{2-7}
%                      & 2                   & 0.5          & 0.25         & 0            & 0            & 0            \\ \cline{2-7}
%                      & 3                   & 0.5          & 0            & 0.25         & 0.5          & 0.75         \\ \cline{2-7}
%                      & 4                   & 0.25         & 0.75         & 0.5          & 0.5          & 0            \\ \hline
%\multirow{4}{*}{3}    & 1                   & 0.25         & 0.25         & 0.5          & 0.25         & 0            \\ \cline{2-7}
%                      & 2                   & 0.25         & 0.25         & 0.5          & 0.25         & 0.5          \\ \cline{2-7}
%                      & 3                   & 0.25         & 0.25         & 0.25         & 0.25         & 0.25         \\ \cline{2-7}
%                      & 4                   & 0.75         & 0.5          & 0.25         & 0            & 0            \\ \hline
%\multirow{4}{*}{4}    & 1                   & 0.5          & 0.25         & 0.25         & 0.25         & 0.25         \\ \cline{2-7}
%                      & 2                   & 0.25         & 0.75         & 0            & 0.5          & 0            \\ \cline{2-7}
%                      & 3                   & 0.25         & 0.25         & 0.5          & 0            & 0            \\ \cline{2-7}
%                      & 4                   & 0.25         & 0.5          & 0.75         & 0.25         & 0.25         \\ \hline
%\multicolumn{2}{|c|}{Mean}                  & 0.421875     & 0.359375     & 0.34375      & 0.28125      & 0.28125      \\ \hline
%\multicolumn{2}{|c|}{Std}                   & 0.1983000672 & 0.2576941016 & 0.2212653008 & 0.2212653008 & 0.2719528145 \\ \hline
%\caption{SAE, {\em last} Test Time with 1 over 10 Re-sampled {\em raw dataset}}
%\label{tbl:sae_last_1_10_time}
%1                     & 4:20:50 & 4:58:12 & 7:44:27 & 6:42:45 & 8:38:18 \\ \hline
%2                     & 3:48:20 & 3:51:03 & 5:16:07 & 6:02:29 & 8:24:17 \\ \hline
%3                     & 3:50:54 & 4:47:55 & 5:03:59 & 6:29:31 & 8:48:47 \\ \hline
%4                     & 3:40:38 & 4:09:14 & 4:56:10 & 6:09:21 & 8:24:11 \\ \hline
%Mean                  & 3:55:11 & 4:26:36 & 5:45:11 & 6:21:02 & 8:33:53 \\ \hline

\subsection{Analysis Training LSTM in {\em second model} and {\em third model}}
The difference between {\em first model} and other models is that other models have AE. Therefore, AE layer from {\em second model} and {\em third model} caused worse performance. The evidence of this can be found during training LSTM in both models. Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show the accuracy of the result from LSTM on each iterations during training. Figure \ref{fig:sae_loss} and Figure \ref{fig:mae_loss} show the loss (error) on each iterations during training.

%Table \ref{tbl:sae_16_accuracy}, Table \ref{tbl:sae_32_accuracy}, Table \ref{tbl:sae_64_accuracy}, Table \ref{tbl:sae_128_accuracy}, and Table \ref{tbl:sae_256_accuracy} show the details of the train accuracy from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Table \ref{tbl:sae_16_loss}, Table \ref{tbl:sae_32_loss}, Table \ref{tbl:sae_64_loss}, Table \ref{tbl:sae_128_loss}, and Table \ref{tbl:sae_256_loss} show the details of the train loss from {\em second model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Table \ref{tbl:mae_16_accuracy}, Table \ref{tbl:mae_32_accuracy}, Table \ref{tbl:mae_64_accuracy}, Table \ref{tbl:mae_128_accuracy}, and Table \ref{tbl:mae_256_accuracy} show the details of the train accuracy from {\em third model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons. Table \ref{tbl:mae_16_loss}, Table \ref{tbl:mae_32_loss}, Table \ref{tbl:mae_64_loss}, Table \ref{tbl:mae_128_loss}, and Table \ref{tbl:mae_256_loss} show the details of the train loss from {\em third model} with 16 neurons, 32 neurons, 64 neurons, 128 neurons, and 256 neurons.

@@

%\caption{SAE, 16 Neuron Training Accuracy}
%\label{tbl:sae_16_accuracy}
%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                \\ \cline{3-11}
%                      &                     & 0             & 120         & 240           & 360          & 480          & 600                              & 720                               & 840          & 960          \\ \hline
%\multirow{4}{*}{1}    & 1                   & 0.58333       & 0.66667     & 0.66667       & 0.75         & 0.75         & 0.83333                          & 1                                 & 0.91667      & 0.91667      \\ \cline{2-11}
%                      & 2                   & 0.5           & 0.5         & 0.66667       & 0.83333      & 0.83333      & 0.91667                          & 1                                 & 1            & 1            \\ \cline{2-11}
%                      & 3                   & 0.41667       & 0.58333     & 0.66667       & 0.91667      & 0.83333      & 0.83333                          & 0.91667                           & 1            & 0.91667      \\ \cline{2-11}
%                      & 4                   & 0.5           & 0.58333     & 0.58333       & 0.58333      & 0.58333      & 0.75                             & 0.91667                           & 0.91667      & 0.91667      \\ \hline
%\multirow{4}{*}{2}    & 1                   & 0.5           & 0.58333     & 0.5           & 0.5          & 0.5          & 0.58333                          & 0.75                              & 0.75         & 0.83333      \\ \cline{2-11}
%                      & 2                   & 0.5           & 0.58333     & 0.75          & 0.75         & 0.83333      & 0.91667                          & 1                                 & 1            & 1            \\ \cline{2-11}
%                      & 3                   & 0.5           & 0.66667     & 0.75          & 0.75         & 0.83333      & 0.91667                          & 0.83333                           & 0.83333      & 0.91667      \\ \cline{2-11}
%                      & 4                   & 0.5           & 0.5         & 0.5           & 0.5          & 0.58333      & 0.5                              & 0.58333                           & 0.66667      & 0.66667      \\ \hline
%\multirow{4}{*}{3}    & 1                   & 0.5           & 0.5         & 0.58333       & 0.58333      & 0.75         & 0.58333                          & 0.58333                           & 0.75         & 0.83333      \\ \cline{2-11}
%                      & 2                   & 0.5           & 0.41667     & 0.5           & 0.66667      & 0.66667      & 0.75                             & 0.75                              & 0.75         & 0.91667      \\ \cline{2-11}
%                      & 3                   & 0.5           & 0.33333     & 0.5           & 0.41667      & 0.5          & 0.58333                          & 0.91667                           & 0.75         & 0.75         \\ \cline{2-11}
%                      & 4                   & 0.33333       & 0.66667     & 0.66667       & 0.66667      & 0.83333      & 0.83333                          & 0.91667                           & 1            & 1            \\ \hline
%\multirow{4}{*}{4}    & 1                   & 0.5           & 0.58333     & 0.58333       & 0.66667      & 0.75         & 0.83333                          & 0.83333                           & 0.83333      & 0.75         \\ \cline{2-11}
%                      & 2                   & 0.5           & 0.33333     & 0.66667       & 0.83333      & 0.66667      & 0.75                             & 0.75                              & 0.66667      & 0.83333      \\ \cline{2-11}
%                      & 3                   & 0.41667       & 0.58333     & 0.66667       & 0.66667      & 0.75         & 0.83333                          & 0.91667                           & 0.91667      & 0.91667      \\ \cline{2-11}
%                      & 4                   & 0.5           & 0.41667     & 0.5           & 0.66667      & 0.75         & 0.75                             & 0.75                              & 0.83333      & 0.75         \\ \hline
%\multicolumn{2}{|c|}{Mean}                  & 0.484375      & 0.531249375 & 0.609375625   & 0.671875625  & 0.713540625  & 0.760415625                      & 0.838541875                       & 0.84895875   & 0.8697925    \\ \hline
%\multicolumn{2}{|c|}{Std}                   & 0.05459200528 & 0.109185219 & 0.08985045449 & 0.1342629486 & 0.1177274886 & \multicolumn{1}{l|}{0.132201113} & \multicolumn{1}{l|}{0.1342647589} & 0.1187071365 & 0.1007786353 \\ \hline
%\end{tabular}}
%\caption{SAE, 32 Neuron Training Accuracy}
%\label{tbl:sae_32_accuracy}
%\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
%\multirow{2}{*}{Test} & \multirow{2}{*}{CV} & \multicolumn{9}{c|}{Iterations}                                                                                                                                                 \\ \cline{3-11}
%                      &                     & 0             & 120          & 240          & 360          & 480          & 600                              & 720                               & 840          & 960           \\ \hline
%\multirow{4}{*}{1}    & 1                   & 0.41667       & 0.66667      & 0.91667      & 0.91667      & 0.83333      & 0.91667                          & 1                                 & 0.91667      & 1             \\ \cline{2-11}
%                      & 2                   & 0.5           & 0.75         & 0.66667      & 0.75         & 0.83333      & 1                                & 1                                 & 1            & 1             \\ \cline{2-11}
%                      & 3                   & 0.5           & 0.75         & 0.66667      & 0.75         & 0.91667      & 1                                & 0.91667                           & 0.58333      & 0.75          \\ \cline{2-11}
%                      & 4                   & 0.5           & 0.58333      & 0.66667      & 0.66667      & 0.91667      & 0.91667                          & 1                                 & 1            & 1             \\ \hline
%\multirow{4}{*}{2}    & 1                   & 0.5           & 0.75         & 0.83333      & 0.83333      & 0.91667      & 1                                & 0.91667                           & 0.91667      & 1             \\ \cline{2-11}
%                      & 2                   & 0.41667       & 0.58333      & 0.83333      & 0.91667      & 1            & 0.91667                          & 1                                 & 0.91667      & 1             \\ \cline{2-11}
%                      & 3                   & 0.5           & 0.66667      & 0.58333      & 0.66667      & 0.66667      & 0.66667                          & 0.75                              & 0.75         & 0.83333       \\ \cline{2-11}
%                      & 4                   & 0.5           & 0.33333      & 0.41667      & 0.5          & 0.5          & 0.83333                          & 0.58333                           & 0.83333      & 0.83333       \\ \hline
%\multirow{4}{*}{3}    & 1                   & 0.33333       & 0.75         & 0.83333      & 0.91667      & 0.91667      & 1                                & 1                                 & 1            & 1             \\ \cline{2-11}
